---
title: "Fatal Accident Report"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{parse_vr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
# library(bbanalyze)
```

Fatality Analysis Reporting System package overview
-----------------------------------------------------

This package is a collection of functions that allows the user to read, process and analyze data provided by the *US National Highway Traffic Safety Administration's* Fatality Analysis Reporting System (FARS)

Details and additional information about FARS is available at the following reference links:

- [FARS](https://www.nhtsa.gov/research-data/fatality-analysis-reporting-system-fars)

Functions
---------

This package includes the following functions:

- make_filename -> Builds the name of the file based on the year
- fars_read_years -> Read all files that correspond to a vector of years
- fars_summarize_years -> Collect and summarize data over multiple years
- fars_map_state -> Generate a map showing the number of measurements in a specified state
